Invasive chameleons released from predation display more conspicuous colors

### 2022-02-22 ms_Sci_Adv.Rmd
MS updated removing random text
Fixed up formatting issues

**Authors**: Martin J. Whiting^1,2^, Brenden S. Holland^3^, J. Scott Keogh^4^, Daniel  W.A. Noble^4^, Katrina J. Rankin^5^ and Devi Stuart-Fox^5^

@@

F_AC_Disp_pop_bgk # Lum object male-male display

F_CC_Disp_pop_bgk # Chrom object male-male display

F_AC_Court_pop_bgk $ Lum object social

F_CC_Court_pop_bgk  # Chromatic object social

@@

```{r figure1, cache=FALSE, fig.cap = "**Chameleon color signal change in response to different social stimuli. Male chameleons experience intense sexual selection**. During the breeding season they change from dull green to a highly conspicuous bright yellow display signal. They also readily fight by locking horns and sometimes pierce their rival’s skin with their horns. **a**, A dominant male in display coloration. **b**, A subordinate male that lost a contest and turned from bright yellow to brown. **c**, Two males fighting, both are in display coloration and relatively even matched. **d**, A courting male in full display color while the female has turned to a contrasting color, rejecting the male. See Supplementary information for additional photos, including in response to a snake"}
library(magick)

@@

```{r figure2, fig.width = 14, fig.height= 14, fig.cap="**Mean spectral reflectance curves for male chameleons for representative body regions (gular, top flank) and background (leaves) for Hawaii and Kenya**. The context for measurement was **a**, male contest displays; **b**, courtship; **c**, bird predator; and **d**, snake predator. More details in online Supplementary Information and Supplementary Fig. 5"}
library(magick)
img <- image_read("./output/figures/Figure3_Nature.png")
img

@@

```{r figure3, cache = FALSE, fig.width = 14, fig.height= 14, fig.cap= "**Chromatic and luminance contrast in Just Noticeable Differences (JND), of Hawaiian and Kenyan chameleons against their respective backgrounds (i.e., average environment of stems and leaves)**. Luminance **a**, and chromatic **b**, contrast of male chameleons during male-male contests and female courtship. JNDs are calculated based on the chameleon visual system. Luminance **c**, and chromatic **d**, contrast of male chameleons during snake and bird predator encounters. JNDs are calculated based on the snake and bird visual systems. Contrasts between means, ‘Beta’, that are bold indicate significant effects."}
rerun = FALSE
if(rerun){
## Make figures that average across body regions, but display Social Context

@@

```{r figure4, cache = FALSE, fig.width = 14, fig.height= 9, fig.cap= "**Evidence for local adaptation of social color signals in both a, chromatic- and b, luminance contrast for Hawaiian chameleons**. For local adaptation, signals are predicted to be more conspicuous against their own background. In this case, Hawaiian chameleons were both significantly more chromatic and brighter (luminance contrast) against their own background compared to the Kenyan background indicating increased local signal conspicuousness."}
rerun=FALSE

>>>>

**Authors**: Martin J. Whiting^1,2,*^, Brenden S. Holland^3^, J. Scott Keogh^4^, Daniel  W.A. Noble^4^, Katrina J. Rankin^5^ and Devi Stuart-Fox^5^

@@

@@

```{r figure1, cache=FALSE, fig.cap = "**Chameleon color signal change in response to different social stimuli. Male chameleons experience intense sexual selection**. During the breeding season they change from dull green to a highly conspicuous bright yellow display signal. They also readily fight by locking horns and sometimes pierce their rival’s skin with their horns. **a**, A dominant male in display coloration. **b**, A subordinate male that lost a contest and turned from bright yellow to brown. **c**, Two males fighting, both are in display coloration and relatively even matched. **d**, A courting male in full display color while the female has turned to a contrasting color, rejecting the male. See Supplementary information for additional photos, including in response to a snake. Photo credit: Martin Whiting, Macquarie University."}
library(magick)

@@

```{r figure2, fig.width = 14, fig.height= 14, fig.cap="**Mean spectral reflectance curves for male chameleons for representative body regions (gular, top flank) and background (leaves) for Hawaii and Kenya**. The context for measurement was **a**, male contest displays; **b**, courtship; **c**, bird predator; and **d**, snake predator. More details in online Supplementary Information and Supplementary Fig. 5. Photo credit: Martin Whiting, Macquarie University."}
library(magick)
img <- image_read("./output/figures/Figure3_Nature.png")
img

@@

```{r figure3, cache = FALSE, fig.width = 14, fig.height= 14, fig.cap= "**Chromatic and luminance contrast in Just Noticeable Differences (JND), of Hawaiian and Kenyan chameleons against their respective backgrounds (i.e., average environment of stems and leaves)**. Luminance **a**, and chromatic **b**, contrast of male chameleons during male-male contests and female courtship. JNDs are calculated based on the chameleon visual system. Luminance **c**, and chromatic **d**, contrast of male chameleons during snake and bird predator encounters. JNDs are calculated based on the snake and bird visual systems. Contrasts between means, ‘Beta’, that are bold indicate significant effects. Photo credit: Martin Whiting, Macquarie University."}
rerun = FALSE
if(rerun){
## Make figures that average across body regions, but display Social Context

@@

```{r figure4, cache = FALSE, fig.width = 14, fig.height= 9, fig.cap= "**Evidence for local adaptation of social color signals in both a, chromatic- and b, luminance contrast for Hawaiian chameleons**. For local adaptation, signals are predicted to be more conspicuous against their own background. In this case, Hawaiian chameleons were both significantly more chromatic and brighter (luminance contrast) against their own background compared to the Kenyan background indicating increased local signal conspicuousness. Photo credit: Martin Whiting, Macquarie University."}
rerun=FALSE

### 2022-02-22 supp.Rmd
Fixed up formatting issues

```{r Figcolsig, fig.align = 'center', fig.cap = "**Additional examples of chameleon color signals and behavior in response to different social contexts**. **(A)** Two different males in conspicuous display color adopted at the start of a contest and retained by the dominant male. **(B)** Two examples of males engaged in horn locking. Males in the bottom panel are evenly matched at this stage and both are in full display color. In the top image, the male on the left is starting to change to a subordinate color. **(C)** Conspicuous yellow-green male courtship color. When females reject males, they develop a heavily contrasting pattern."}
figs1 <- image_read("./output/figures/FigS1.png")
figs1

@@

```{r Figcolsig2, fig.align = 'center', fig.cap = "**Representative photos of habitat in Kenya (A, B) and Hawaii (C, D)**. In both sites, chameleons favored well-vegetated trees and bushes, often with lots of vines."}
figs2 <- image_read("./output/figures/FigS2.jpg")
figs2

@@

```{r Figcolsig3, fig.align = 'center', fig.cap = "**The experimental setup for behavioral trials**. We constructed a platform of three connected horizontal perches in a triangle, thereby always allowing an individual to escape a rival or if a female, a courting male. The male on the left won this contest and is in full display color while the male on the right has lost this contest and turned brown (subordinate)."}
figs3 <- image_read("./output/figures/FigS3.jpg")
figs3

@@

```{r Figcolsig4, fig.align = 'center', fig.width = 12, fig.height = 12, fig.cap = "**We presented chameleons with model snake and bird predators to elicit an anti-predator response, particularly, color change, to test the hypothesis that character release in Hawaii would also result in a signal more conspicuous to a predator**. **(A)** A model snake (*Dispholidus typus*) causing a characteristic contrasting color change and **(B)** a model bird (*Aviceda cuculoides*) which was flown over the top of the chameleon."}
figs4 <- image_read("./output/figures/FigS4.jpg")
figs4

@@

```{r Figcolsig5, fig.align = 'center', fig.width = 12, fig.height = 12, fig.cap = "**Location of body regions we measured for spectral reflectance**. See details in text."}
figs5 <- image_read("./output/figures/FigS5.jpg")
figs5

>>>>

```{r Figcolsig, fig.align = 'center', fig.cap = "**Additional examples of chameleon color signals and behavior in response to different social contexts**. **(A)** Two different males in conspicuous display color adopted at the start of a contest and retained by the dominant male. **(B)** Two examples of males engaged in horn locking. Males in the bottom panel are evenly matched at this stage and both are in full display color. In the top image, the male on the left is starting to change to a subordinate color. **(C)** Conspicuous yellow-green male courtship color. When females reject males, they develop a heavily contrasting pattern. Photo credit: Martin Whiting, Macquarie University."}
figs1 <- image_read("./output/figures/FigS1.png")
figs1

@@

```{r Figcolsig2, fig.align = 'center', fig.cap = "**Representative photos of habitat in Kenya (A, B) and Hawaii (C, D)**. In both sites, chameleons favored well-vegetated trees and bushes, often with lots of vines. Photo credit: Martin Whiting, Macquarie University."}
figs2 <- image_read("./output/figures/FigS2.jpg")
figs2

@@

```{r Figcolsig3, fig.align = 'center', fig.cap = "**The experimental setup for behavioral trials**. We constructed a platform of three connected horizontal perches in a triangle, thereby always allowing an individual to escape a rival or if a female, a courting male. The male on the left won this contest and is in full display color while the male on the right has lost this contest and turned brown (subordinate). Photo credit: Martin Whiting, Macquarie University."}
figs3 <- image_read("./output/figures/FigS3.jpg")
figs3

@@

```{r Figcolsig4, fig.align = 'center', fig.width = 12, fig.height = 12, fig.cap = "**We presented chameleons with model snake and bird predators to elicit an anti-predator response, particularly, color change, to test the hypothesis that character release in Hawaii would also result in a signal more conspicuous to a predator**. **(A)** A model snake (*Dispholidus typus*) causing a characteristic contrasting color change and **(B)** a model bird (*Aviceda cuculoides*) which was flown over the top of the chameleon. Photo credit: Martin Whiting, Macquarie University."}
figs4 <- image_read("./output/figures/FigS4.jpg")
figs4

@@

```{r Figcolsig5, fig.align = 'center', fig.width = 12, fig.height = 12, fig.cap = "**Location of body regions we measured for spectral reflectance**. See details in text. Photo credit: Martin Whiting, Macquarie University."}
figs5 <- image_read("./output/figures/FigS5.jpg")
figs5
